\Huge Conferences in an Era of Expensive Carbon

### 2019-06-17 main.tex
CP

>>>>

\begin{itemize}
\item Accountability.
  \begin{itemize}
  \item Proposal: Every ACM-sponsored conference should be required to
  publicly report its carbon footprint (total and per-participant).
  (Including PC meetings, participant travel, maybe hotel?).
  \item ACM needs to provide tools to help conferences do this.
  \item Benefits:
  \begin{itemize}
  \item Encourages people to pay attention, which will lead to some changes
  in behavior all by itself. 
  \item Generates data that will be needed for grounding discussions of how
  optimize footprint.
  \item Indeed, optimizing footprint is not so easy.  (Describe some of our
  data.)  More data and thorough analysis is needed.
  \end{itemize}
  \end{itemize}
\item Pricing carbon.
  \begin{itemize}
  \item To motivate more painful changes and force people to make decisions,
  we need a price on carbon.
  \item Ultimately, we want/expect governments to do this.  But we don't need to
  wait. 
  \item Proposal: ACM should apply downward pressure on conferences by
  charging conferences a surcharge based on their carbon footprint.
  \item This money can be used in many ways: buying carbon offsets,
  supporting ``green research'', supporting virtualizing conferences
  (livestreaming, etc.), supporting a transition to a low-carbon / few
  conferences business model for ACM.
  \end{itemize}
\end{itemize}
